%-------------------------
% Resume in Latex
% Author: Anshumaan Kumar Prasad
% Website: https://github.com/aminoxix/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\usepackage{xcolor}
\hypersetup{colorlinks,urlcolor=blue}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% ----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
% \usepackage{times}
% \usepackage{helvet}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\project}[2]{
\textbf{}{
\href{#2}{{#1} \,\faExternalLink}
}
    \hfill
}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\project{#1}{#2}
{#3}\\ \vspace{-1pt}}

\newcommand{\resumeItemHeading}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubHeading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemHeadingStart}{\begin{itemize}}
\newcommand{\resumeItemHeadingEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{}{\faUser ~ \Large Anshumaan Kumar Prasad}} & \faEnvelope ~ Email: \href{mailto:contact@aminoxix.me}{contact@aminoxix.me}\\
	\faGlobe ~ \href{https://aminoxix.me/}{aminoxix.me} & \faPhone ~ Mobile: \href{tel:+91 9425200288}{+91-94252-00288} ~ ~ ~ ~\\
\end{tabular*}

% \begin{center}
%     \small
%     \faGithub \href{https://github.com/aminoxix}{\raisebox{-0.2\height}\ github.com/aminoxix} ~
%     \faLinkedin \href{https://linkedin.com/in/aminoxix}{\raisebox{-0.2\height}\ linkedin.com/in/aminoxix} ~
%     \vspace{-13pt}
% \end{center}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubHeading
{Shri Shankaracharya Technical Campus}{Bhilai, IN}
{Bachelor of Technology in Information Technology;  GPA: 3.26 (7.7/10.0)}{Aug. 2019 -- July 2023}
\resumeSubHeadingListEnd
  
%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubHeading
{Xamtac Consulting LLC $|$ \href{https://xamtac.com}{xamtac.com}}{Remote, Chicago, Illinois}
{Frontend Developer - Intern}{June 2023 - Present}
\resumeItemListStart
\resumeItem{Languages \& Tools: }{TypeScript, Next.js, Mantine UI, React, Tailwind CSS, tRPC, Asana}
\resumeItem{}
{Developing a SaaS Application for marketing agency automation, incorporating an efficient \href{https://form-stepper.vercel.app/}{Onboarding client (stepper) form} and a Leads - CRM feature to streamline lead management for and across the organizations.}
\resumeItem{}
{Initiating and supporting customized client solutions for diverse products and services, resulting in a remarkable 10x improvement in productivity.}
\resumeItem{}
{Collaborating with peers engineers \& figma designers to solve technical problems and merge requests}
\resumeItemListEnd
\vspace{1.5pt}
\resumeSubHeading
{Pillar Project Worldwide Limited $|$ \href{https://pillar.fi}{pillar.fi}}{Remote, London \& Wales, ENG}
{Junior Frontend Developer}{June 2022 - Nov 2022}
\resumeItemListStart
\resumeItem{Languages \& Tools: }{TypeScript, Next.js, React, Blocknative, Web3, Etherspot SDK, Zeplin, Linear App}
\resumeItem{}
{Agile mode, UK estimation, take part in agile ceremonies and daily dev standups}
\resumeItem{Etherspot Dashboard: }{The \href{https://develop.etherspot.io}{Etherspot Dashboard} is an all-in-one, EVM-compatible platform that allows users to interact seamlessly with multiple assets and protocols — all without having to switch networks.}
\resumeItemListStart
\resumeItem{Notifications: }
{Service for sending toast, push and in-app notifications involved in features such as transactions (send \& deposit), network switch and authentication.}
\vspace{1.2pt}
\resumeItem{Data Visualization: }
{Representation of tokens to a whole of connected wallet in the form of the doughnut chart.}
\resumeItem{UI Optimization: }
{Developed loading state, Sentry Integration, Debugging dashboard \& fixing bugs.}
\resumeItemListEnd
\vspace{5pt}
\resumeItem{Pillar Staking Website: }{A \href{https://ui-modifications.pillar-staking-frontend.pages.dev/}{staking website} to stake between 10,000 and 250,000 \$PLR to be eligible to receive rewards, built using smart contract via ABI (Application Binary Interface) interaction. Tokens staked are locked for a minimum period of 1 year. Rewards are paid out in wETH.}
\vspace{3pt}
\resumeItemListEnd
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\item{
      \textbf{Tools: }{Vercel, Railway, tRPC, PostgreSQL, MySQL \& Figma}
      \hfill
      \textbf{Languages: }{Javascript \& TypeScript}}
\vspace{-7pt}
\item{
      \textbf{Frameworks: }{React, Node, Next, Tailwind, Mantine \& Bootstrap}
      \hfill
      \textbf{Cloud: }{MongoDB Atlas \& Google Cloud}}
\resumeSubHeadingListEnd
 
%-----------PROJECTS-----------------
\section{Projects}
\projectHeading{\textbf{Boilerplate Web App} $|$ Vite $+$ Firebase}{https://boilerplatewebapp.vercel.app}{Mar 2022}
\vspace{-5pt}
\resumeItemListStart
\resumeItem{}{This website was designed to streamline the app development process for developers by offering customizable layouts and a modern, user-friendly navigation bar. Its login, signup, calculator, and notification generator features enhance the user experience across multiple screens.}
\vspace{-5pt}
\resumeItem{What I learnt: }{Vanilla JavaScript, Local Storage, Strings, Arrays \& their in-built methods}
\resumeItemListEnd
\vspace{4pt}
\projectHeading{\textbf{Quiz App} $|$ React $+$ Vite (pnpm)}{https://github.com/quizlabs/v0}{Jan - Feb 2023}
\vspace{-5pt}
\resumeItemListStart
\resumeItem{}{Developed a dynamic and user-friendly frontend UI for a Quiz App, leveraging Sequelize for seamless integration with the backend and laying the foundation for future enhancements using Node.js \& Express.js.}
\vspace{-5pt}
\resumeItem{What I learnt: }{Global State Management and hooks such as useEffect, useState \& useRef}
\resumeItemListEnd

%--------EXTRACURRICULAR ACTIVITY------------
\section{Extracurricular Activity}
\resumeSubHeadingListStart
\resumeSubHeading
{DEVSTRONS' $|$ \href{https://devstrons.org}{devstrons.org}}{Community}
{Community Founder}{July 2021 - Present}
\resumeItemListStart
\resumeItem{}{Mentored 500+ people while holding positions such as Postman Student Leader, CNCF Organizer, Hack Club Leader, and Blogger}
\resumeItem{}{Introduced the first student-run debugging contest with a \href{https://bit.ly/bugtrons2-con}{conference}, BUGTRONS, to empower coders to get influenced by developing software, enhancing skills, eradicating bugs \& the pursuit of new prospects.}
\resumeItemListEnd
\vspace{2pt}
\item{
      \textbf{Open Source Contributions}{}
      \vspace{-7pt}
      \hfill
      \textbf{}{Jan 2021 - Present}
}
\resumeItemListStart
\item \href{https://github.com/jenkins-x/jx-docs/pull/3381}{{fix: [Docs/Bug] Mobile view updated} \,\faExternalLink}
\vspace{-3pt}
\item \href{https://github.com/meshery/meshery/pull/3070}{{[Docs] mesheryctl pattern delete page added} \,\faExternalLink}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
